**The status of the microbial census: an update**

### 2015-12-05 results/tables/build_bacterial_culture_effort_table.Rmd
Add supplemental tables describing culturability

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=1.0in
---

@@

data <- read.table(file="data/process/archaea.cultured_by_time_counts.tsv", header=T, stringsAsFactors=F)

all <- data[,grepl("all_", colnames(data))]
all$all_uncult_nseqs <- all$all_total_nseqs - all$all_cult_nseqs
all$all_uncult_sobs <- all$all_total_sobs - all$all_cult_sobs

@@

caption <- "\\textbf{Supplementary Table 7. Frequency that each archaeal sequence or OTU was retrieved by cultivation or by culture-independent methods.}"

>>>>

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=0.2in
---

@@

data <- read.table(file="data/process/bacteria.cultured_by_time_counts.tsv", header=T, stringsAsFactors=F)
data <- data[!rownames(data) %in% "aquifer1",]
all <- data[,grepl("all_", colnames(data))]
all$all_uncult_nseqs <- all$all_total_nseqs - all$all_cult_nseqs
all$all_uncult_sobs <- all$all_total_sobs - all$all_cult_sobs

@@

caption <- "\\textbf{Supplementary Table 6. Frequency that each bacterial sequence or OTU was retrieved by cultivation or by culture-independent methods.}"
